Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-29 doc/main_jfm.tex
adding caption of Fig.1

\begin{figure}
\centering
\includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
\includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
\includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
  \caption{}
    \label{figure:permeability}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
\includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
\includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
  \caption{JP vesicle are suspended in a quiescent flow for relaxations where the reference arc lengths $L_0$ are $107$ nm and $141$ nm with particle diameters $2.5$ nm and $1.25$ nm, respectively. (a) The arc length $L$ decreases over time where the dashed curves represent the data and solid curves are linear fits; (b) A linear relationship between $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear relationship between aqueous flux $dA/dt$ and $L\Delta p$. For panels (b) and (c), the cross symbols are numerical results and fit by using solid lines.}
    \label{figure:permeability}
\end{figure}
